The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-16 dit-paper_ieee.tex
review algo 1

\begin{abstract}
	Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
	conditions in the case of small changes in task parameters, such as when porting a system to a
	different platform. The C-space describes the
	set of execution times for which a system is feasible. This paper extends previous works to
	generalize the description of the C-space for Earliest Deadline First scheduling to
	systems with initial task offsets. The feasibility gain offered by offsets is
	then expressed as the volume ratio between the C-space of an asynchronous system and its corresponding
	synchronous system.
\end{abstract}

@@

		For those systems, the preemptive \emph{Earliest Deadline First} (EDF) algorithm, in
		which jobs are prioritized according to their absolute deadline, has been
		shown to be optimal \cite{liu1973scheduling}, which means it
		correctly schedules any feasible system within that group.

@@

  The value of the first DIT can be found by solving the following modular equation system:
  \[
    t_d = \min
    \left( t \; s.t. \; \forall i:
      \left\{
        \begin{array}{c}
          t > 0 \\
          t \equiv a_i \; (mod \; T_i) \\
          a_i \in [D_i, T_i]
        \end{array}
      \right.
    \right)
  \]
  The authors of \cite{george2009characterization} give a method to solve this system for cases in which periods are pairwise coprime.

@@

		\begin{algorithm}
			\caption{Modified Gauss Algorithm}
			\label{alg:multiACRP}
			\begin{algorithmic}[1]
				\REQUIRE $A$ is a list of the sets of possible $a_i$ per task
				\REQUIRE $H$ is the hyperperiod of the system

				\STATE $sumchunks \leftarrow \text{empty list}$
				\FORALL{$\tau_j \in \tau$}
					\STATE $taskTerms \leftarrow \text{empty list}$
					\STATE $Mj \leftarrow \frac{H}{T_j}$
					\STATE $invMj \leftarrow Mj^{-1} (mod \; T_j)$
					\FORALL{$a_i \in A(\tau_j)$}
						\STATE $\text{append} \; (a_i \cdot Mj \cdot invMj) \; \text{to} \; taskTerms$
					\ENDFOR
					\STATE $\text{append} \; taskTerms \; \text{to} \; sumchunks$
				\ENDFOR

				\STATE $results \leftarrow \text{empty list}$
				\STATE append $0$ to $results$
				\FORALL{$\tau_j \in \tau$}
					\STATE $newresults \leftarrow \text{empty list}$
					\FORALL{$a_i \in A(\tau_j)$}
						\FORALL{$r \in results$}
							\STATE $\text{append} \; (r + sumchunks(\tau_j,i)) \; \text{to} \; newresults$
						\ENDFOR
					\ENDFOR
					\STATE $results \leftarrow newresults$
				\ENDFOR
				\RETURN $r \; (mod \; H)$ for all $r \in results$
			\end{algorithmic}
		\end{algorithm}

>>>>

\begin{abstract}
	Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
	conditions in the case of small changes in task parameters, such as when porting a system to a
	different platform. The C-space describes the set of execution times for which
	a system is feasible. This paper extends previous works to generalize the
	description of the C-space for Earliest Deadline First scheduling to systems
	with initial task offsets. The feasibility gain offered by offsets is then
	expressed as the volume ratio between the C-space of an asynchronous system and
	its corresponding synchronous system. The problem requires solving multiple
	similar instances of the Chinese Remainder Problem, for which an algorithm
	efficient in this context is provided.
\end{abstract}

@@

		For both synchronous and asynchronous systems, the preemptive
		\emph{Earliest Deadline First} (EDF) algorithm, in which jobs are prioritized according to their absolute deadline, has been
		shown to be optimal \cite{liu1973scheduling}, which means it
		correctly schedules any feasible system within that group.

@@

  The value of the first DIT can be found by solving the following modular equation system:
	\[
		t_d = \min
		\left( t \; s.t. \; \forall i \; \exists a_i \in [D_i, T_i]:
			\left\{
				\begin{array}{c}
					t > 0 \\
					t \equiv a_i \; (mod \; T_i) \\
				\end{array}
			\right.
		\right)
	\]
  The authors of \cite{george2009characterization} give a method to solve this system for cases in which periods are pairwise coprime.

@@

		\begin{algorithm}
			\caption{Modified Gauss Algorithm}
			\label{alg:multiACRP}
			\begin{algorithmic}[1]
				\REQUIRE $\forall j: A_j$ is a list of the sets of possible $a_i$ values for
				task $\tau_j$ 
				\REQUIRE $H$ is the hyperperiod of the system

				\STATE $sumchunks \leftarrow \text{empty list}$
				\FORALL{$\tau_j \in \tau$}
					\STATE $taskTerms \leftarrow \text{empty list}$
					\STATE $Mj \leftarrow \frac{H}{T_j}$
					\STATE $invMj \leftarrow Mj^{-1} (mod \; T_j)$
					\FORALL{$a_i \in A_j$}
						\STATE $taskTerms[i] \leftarrow (a_i \cdot Mj \cdot invMj)$
					\ENDFOR
					\STATE $sumchunks[j] \leftarrow taskTerms$
				\ENDFOR

				\STATE $results \leftarrow \text{empty list}$
				\STATE append $0$ to $results$
				\FORALL{$\tau_j \in \tau$}
					\STATE $newresults \leftarrow \text{empty list}$
					\FORALL{$a_i \in A_j$}
						\FORALL{$r \in results$}
							\STATE $\text{append} \; (r + sumchunks[j][i]) \; \text{to} \;
							newresults$
						\ENDFOR
					\ENDFOR
					\STATE $results \leftarrow newresults$
				\ENDFOR
				\RETURN $r \; (mod \; H)$ for all $r \in results$
			\end{algorithmic}
		\end{algorithm}
